### 2009-12-18 trunk/Papers/reasoning-challenges/conclusion.tex
a first complete draft

This new approach has advantages for each of the three groups of people involved in a competition, the organisers, the participants, and the audience (which usually includes organisers and participants).

@@

@@

>>>>

\todo{this is cut and paste from Guido's text, which I like but which
  was in a different place. The conclusion should be cleaned up and
  made real text. - ak}

This new approach has advantages for each of the three groups of
people involved in a competition, the organisers, the participants,
and the audience (which usually includes organisers and
participants). \todo{do we want to use the term ``stakeholders'' for
  all of these people together? - ak}

@@

\todo{I don't think we should have acknowledgments in the anonymous
  version. - ak}

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2009-12-18 trunk/Papers/reasoning-challenges/levels.tex
a first complete draft

A second social networking tool which we believe would be useful in
the context of a planning evaluation website is to let users tag
problem classes and vote on them.  Any registered user can be allowed
to comment on any problem class and vote for how relevant, important,
or exciting they find it -- say, using a one to five star system as on
Amazon.  This has a number of crucial advantages.  First, an incoming
user or a competition organizer can take the average score as an
indication for the problems that are considered important in the
community.  Next to the difficulty of problems, this can be another
factor in the selection of problem classes for a competition snapshot.
Second, a relevance score for problem classes can also serve as a
guideline for the scheduling of planner runs: Assuming that there is
not enough computing power to run all incoming planners on all domains
in real time (e.g., just before a competition deadline), the runs on
popular domains can be prioritized.

@@

implementing software

>>>>

A second social networking tool which we believe would be useful in
the context of a planning evaluation website is to let users tag
problem classes and vote on them.  Any registered user can be allowed
to comment on any problem class and vote for how relevant, important,
or exciting they find it -- say, using a one to five star system as on
Amazon.  This has a number of crucial advantages.  First, an incoming
user or a competition organizer can take the average score as an
indication for the problems that are considered important in the
community; imagine a ``top ten'' list of domains and planners on the
website's front page.  Next to the difficulty of problems, this can be
another factor in the selection of problem classes for a competition
snapshot.  Second, a relevance score for problem classes can also
serve as a guideline for the scheduling of planner runs: Assuming that
there is not enough computing power to run all incoming planners on
all domains in real time (e.g., just before a competition deadline),
the runs on popular domains can be prioritized.

\section{Evaluation measures}

The continuous evaluation infrastructure we just presented is
fundamentally agnostic to the type of concrete evaluation measures
that it collects.  In particular, traditional measures such as the
percentage of problems solved per system, average solution quality,
average runtime and memory use, and search tree sizes can be
collected -- with the caveat that the virtual machine must be
configured so as to allow comparable runtime measurements.
Furthermore, popularity scores from the social networking aspect can
be incorporated, or different measures could be combined into an
overall score.

@@

On the other hand, we expect that implementing the software for
running the continuous evaluation and presenting the results on a
website would not be a prohibitive effort either.  Most of the
components of the system (continuous integration server, virtual
machines, Wiki) already exist as open-source off-the-shelf
components.  We estimate that a prototype implementation of a complete
system could be built in a person-month of work; surely this is the
amount of work for which funding or volunteers could be found.

\section{Applicability and limitations}

One advantage of the evaluation infrastructure proposed above is that
its applicability is not limited to the evaluation of planners.  Many
reasoning tasks, including constraint solving and theorem proving, are
being evaluated by running solvers over problem instances and
reporting performance measures.  At the level of abstraction at which
our continuous evaluation system could be implemented, there is no
fundamental difference between the problem type ``propositional
planning problem in PDDL 1.0'' and the problem type ``\todo{something
  from CP or similar}'' -- in both cases, the system can collect
problem classes and instances of this type and run them through
solvers that declare themselves to accept such inputs.  This means
that there is a potential for sharing development and maintenance
costs for the evaluation platform among different communities.

However, there are of course limitations to the type of problem for
which it makes sense to run a community-driven continuous evaluation.
For one thing, it must be acceptable in the community that every
system runs on the same hardware and software configuration, as
implemented in the virtual machine images.  On the other hand, our
system makes most sense where the ratio of problem classes to systems
is relatively high.  Neither of the two is true, for instance, for
most natural language processing competitions: Different research
groups tend to use a variety of programming languages and development
environments to build their systems, and there are typically many more
systems in any competition than there are problem classes (corpora).
However, our approach is completely consistent with the requirements
of a community where solving a single hard problem instance for the
first time counts as an achievement, such as in theorem proving.
